Paper changepoint

### 2019-01-09 paper-comparison/compare-christensen.Rmd
update compare-christensen
Correct typo in paper changepoint model selection
6 cpts is not, in fact, ever the best model.

All the models found 4 changepoints (although the paper model actually finds lower deviances for 6 changepoints, 6 was outside the range considered by the paper/anticipated by LDATS, so I'm sticking with 4 for now)

@@

>>>>

All the models found 4 changepoints.

@@

All of the outcomes are reasonably close.

The choice of changepoint model seems to matter less than the choice of LDA model.

### 2019-01-09 paper-comparison/paper_changepoint.Rmd
Correct typo in paper changepoint model selection
6 cpts is not, in fact, ever the best model.

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))

# lowest deviance is for 4 (or 6) changepoints

rm(list = c('cp_results_rodent', 'cp_results_rodent2', 
            'cp_results_rodent3', 'cp_results_rodent5'))
hist(year_continuous[cp_results_rodent4$saved[,1,]],breaks = seq(1977,2016,.25),xlab='',main='Changepoint Estimate')
hist(year_continuous[cp_results_rodent6$saved[,1,]],breaks = seq(1977,2016,.25),xlab='',main='Changepoint Estimate')

@@

## 6 cpts 
annual_hist(cp_results_rodent6,year_continuous)
# turn changepoint results into data frame
df_6 = as.data.frame(t(cp_results_rodent6$saved[,1,])) %>% melt()
df_6$value = year_continuous[df_6$value]

# find 95% confidence intervals on each changepoint:
quantile(df_6[df_6$variable=='V1','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V2','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V3','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V4','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V5','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V6','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')

@@

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))

# lowest deviance is again for 4 (or 6) changepoints

rm(list = c('cp_results_rodent', 'cp_results_rodent2', 
            'cp_results_rodent3', 'cp_results_rodent5'))
hist(year_continuous[cp_results_rodent4$saved[,1,]],breaks = seq(1977,2016,.25),xlab='',main='Changepoint Estimate')
hist(year_continuous[cp_results_rodent6$saved[,1,]],breaks = seq(1977,2016,.25),xlab='',main='Changepoint Estimate')

@@

## 6 cpts 
annual_hist(cp_results_rodent6,year_continuous)
# turn changepoint results into data frame
df_6 = as.data.frame(t(cp_results_rodent6$saved[,1,])) %>% melt()
df_6$value = year_continuous[df_6$value]

# find 95% confidence intervals on each changepoint:
quantile(df_6[df_6$variable=='V1','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V2','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V3','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V4','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V5','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
quantile(df_6[df_6$variable=='V6','value'],probs=c(.025,.975)) %>% date_decimal() %>% format('%d-%m-%Y')
```

>>>>

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(6+1)+(6))

# lowest deviance is for 4 changepoints

rm(list = c('cp_results_rodent', 'cp_results_rodent2', 
            'cp_results_rodent3', 'cp_results_rodent5',
            'cp_results_rodent6'))
hist(year_continuous[cp_results_rodent4$saved[,1,]],breaks = seq(1977,2016,.25),xlab='',main='Changepoint Estimate')

@@

@@

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(6+1)+(6))

# lowest deviance is again for 4 changepoints

rm(list = c('cp_results_rodent', 'cp_results_rodent2', 
            'cp_results_rodent3', 'cp_results_rodent5',
            'cp_results_rodent6'))
hist(year_continuous[cp_results_rodent4$saved[,1,]],breaks = seq(1977,2016,.25),xlab='',main='Changepoint Estimate')

@@

```
